Ultrafast Electron Microscopes: Design Criteria, Electron Sources, and Column Modeling

### 2013-04-14 main.tex
Fixed grammar in Summary

\summary
Dynamic Transmission Electron Microscopy, and its picosecond/femtosecond subclass Ultrafast Electron Microscopy, is an emerging field in intrumentation science.
It attempts to combine the nanoscale spatial resolution of transmission electron microscopes with the temporal resolution of modern ultrafast lasers.
In this thesis I present my contributions to this young field. 
These include a novel model for simulating the dynamics of ultrafast electron pulses in electron microscope systems,
design critera for constructing such a system, and theoretical and experimental groundwork geared towards selecting a useful photocathode for electron generation.
I also present the prototype ultrafast electron microscope system being built at UIC.

>>>>

\summary
Dynamic Transmission Electron Microscopy, and its picosecond/femtosecond subclass Ultrafast Electron Microscopy, is an emerging field in intrumentation science.
It attempts to combine the nanoscale spatial resolution of transmission electron microscopes with the temporal resolution of modern ultrafast lasers.
In this thesis, I present my contributions to this young field. 
These include a novel model for simulating the dynamics of ultrafast electron pulses in electron microscope systems,
design criteria for constructing such a system, and theoretical and experimental groundwork geared towards selecting a useful photocathode for electron pulse generation.
I also present the prototype ultrafast electron microscope system being built at UIC.
